---
title: "FairBnB"
output: 
  html_document:
    citation_package: biblatex
bibliography: "C:/Users/fatbo/OneDrive/Documents/GitHub/Final_PPA/Bibli.bib/airbnb.bib"
biblio-style: "chicago-notes"
date: "2023-12-01"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load, include=FALSE, class.source = 'fold-show'}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(sf)
library(stargazer)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(kableExtra)
library(grid)
library(viridisLite)
library(viridis)
library(gridExtra)
library(jtools)
library(ggcorrplot) 
library(corrr)      
library(kableExtra)
library(jtools)     
library(ggstance) 
library(ggpubr)   
library(broom.mixed) 
options(scipen = 999)

install.packages("png")
library(png)

root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

census_api_key("a6d692af505769f28e39a3ac16b7dcbacb1dad58", overwrite = TRUE)

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")

palette6 <- c("#25CB10", "#5AB60C", "grey40",   "grey40", "#FA7800")

airbnb_color <- c("#FF5A5F")

theme_update(plot.title = element_text(hjust = 0.5))
```

# Intro

Overtourism is a polarizing issue plaguing the city of Amsterdam,
sparking widespread debate and concern among both residents and
policymakers.[^1] Overtourism is defined as a situation in which too
many t[^2]ourists travel to a popular destination, causing the place to
suffer negative environmental, economic, and sociocultural impacts.[\^4]
In 2019, the number of tourists to Amsterdam inhabitants was a
staggering 2,341% (figure 1), indicating that for every local there were
roughly 23 tourists.[\^1] This disproportionate influx has led to
tourism-based gentrification in Amsterdam, a phenomenon where residents
are displaced as services and housing are increasingly tailored to meet
tourist demands rather than those of the local population. The resulting
consequences have been significant, manifesting in a dwindling housing
stock, spiraling rental prices (Figure 2), and an increase in noise
ordinances and public disturbances.[\^2]

[^1]: DutchNews.nl. 2022. "Airbnb-Style Rentals Harmful to
    Amsterdam,Says Tourism Chief."
    <https://www.dutchnews.nl/2022/10/airbnb-style-rentals-harmful-to-amsterdam-says-tourism-chief/>.

[^2]: DutchNews.nl. 2022. "Airbnb-Style Rentals Harmful to
    Amsterdam,Says Tourism Chief."
    <https://www.dutchnews.nl/2022/10/airbnb-style-rentals-harmful-to-amsterdam-says-tourism-chief/>.

![Figure 1. Amsterdam's number of inhabitants vs inbound
overnight](Presentation%20graphics/markdown_graphics/pop.png){width="8.6in"}

![Figure 2. Average rent price of residential property in major
Netherlands
cities](Presentation%20graphics/markdown_graphics/AVG_RENT.png)

The dramatic surge in tourist numbers has unsurprisingly correlated with
a rise in short-term rental accommodations, including Airbnb listings,
which have grown exponentially over the years. This growth is
underscored by the rise in Airbnb guests throughout the Netherlands,
from 75,000 in 2012 to 1.6 million in 2017.[\^2] Specifically, within
Amsterdam itself, Airbnb property listings have skyrocketed from 2,400
listings in 2012 to an overwhelming 19,619 by 2019 [\^4], reflecting the
platform's substantial impact on the city's housing market.

*listing graph*(Figure3)

*listing map?*

To mitigate the mounting pressures from the influx of Airbnb listings
and the consequent housing issues, Amsterdam took proactive steps by
becoming the world's first city to establish regulations on Airbnb
rentals, forming a partnership with the platform itself. This pioneering
move aimed to regulate the short-term rental market that had, until
recently operated with little oversight, aims to address the community's
concerns over noise disturbances, the shrinking supply of residential
housing, and the preservation of neighborhood character.[\^2] These
regulations include.

-   **Listings cannot be rented out for more than 30 days a year**: If
    listings reach or go over their yearly allotment of rental days the
    city of Amsterdam can request that Airbnb block out the listings
    calendar for the remainder of the year.[\^6]

-   **Hosts cannot rent out multiple properties**: Hosts are not allowed
    to rent out additional properties such as summer houses, tents, or
    houseboats.[\^6][\^7]

-   **All listings must have a permit and registration number**: In
    order homes to be listed on Airbnb hosts need to obtain a vacation
    rental permit from the city of Amsterdam. These permits are
    temporary and must be renewed annually.[\^6][\^7]

-   **Rental must be the hosts main residence**: The host must be
    registered as living at the listing address in the Personal Records
    Database (BRP) of the municipality of Amsterdam.[\^6][\^7]

-   \*\* Notification of booking\*\*: According to Amsterdam Housing
    Regulations hosts are required to notify the city every time they
    rent out their home prior to the first day of check in.[\^6][\^7]

-   **Housing corporation and social housing rentals cannot be listed**:
    Rental properties from housing corporations, social housing, or rent
    controlled apartments may not be listed as Airbnb rentals.[\^6][\^7]

\*FairBNB logo\*\*

While Amsterdam has taken a step forward by establishing these
regulations, the city's next challenge lies in developing and
implementing effective monitoring and enforcement mechanisms to ensure
that these regulations address the challenges posed by short-term
rentals and their contribution to overtourism. Given the complexities
associated with the regulation of Airbnb and similar platforms, it
becomes imperative for Amsterdam to explore innovative solutions that
can effectively bridge the gap between policy and enforcement. Fairbnb
emerges as groundbreaking app crafted to align with Amsterdam's
regulatory framework. This application is not merely a response to the
existing challenges, but a forward-thinking approach designed to
complement and enhance the city's efforts in regulating short-term
rentals. Fairbnb's features enable precise tracking of rental days,
ensures hosts adhere to the one-rental property rule, and introduces a
new fair-market pricing feature accompanied by an additional policy
recommendation.

**tracking Rental days**

Fairbnb is designed to meticulously monitor listings to ensure they do
not exceed the 30-day annual rental allotment. This is achieved through
a comprehensive tracking system that utilizes data provided by the city
of Amsterdam, directly from Airbnb, and additional information obtained
through web scraping. The app features a state-of-the-art alert system
that informs the city of Amsterdam about listings that are approaching,
have reached, or have exceeded the 30-day limit. Once a listing reaches
this threshold, Fairbnb will promptly notify Airbnb, enabling them to
block the listing's calendar for the remainder of the year.

*Insert graphics*

**tracking Multiple Rental Properties** Fairbnb is also designed to
identify hosts who list multiple properties by utilizing an advanced
detection system that analyzes data provided by the city of Amsterdam,
Airbnb, and additional data collected with web-scraping techniques. By
cross-referencing this information, the app can accurately pinpoint
hosts who might be in violation of the one-property rule. Upon
identifying such cases, Fairbnb sends notifications to the city
authorities, providing them with detailed insights about potential
violations. In addition, the app communicates with Airbnb to initiate
appropriate actions against these listings.

*Insert graphics*

\*\* new fair-market pricing\*\* Beyond assisting in the monitoring and
enforcement of existing regulations, Fairbnb proposes an innovative
addition: a fair pricing regulation, supported by a corresponding
feature within the app. This initiative focuses on monitoring and
curbing price gouging in Airbnb rentals, serving as a deterrent for
hosts contemplating short-term rentals, thereby aiding in alleviating
the issues of shrinking housing stock and overtourism. The proposed
system will leverage historical Airbnb listing and pricing data,
complemented by data obtained through web scraping, to establish a
fair-market daily rental price. The mechanics of this advanced
fair-market pricing system will be elaborated further in the
methodologies section of the proposal. *Insert graphics*

# Data

## Data Import

## Data Wrangling

```{r joined_nhood sf}
# Joining data sets, converting to crs
attraction_distance <- attraction_distance %>% transform(zipcode = as.character(zipcode))

listings <- left_join(listings, listings_details, by = "id", suffix=c("", ".y")) %>% select(-ends_with(".y"))

listings <- left_join(listings, attraction_distance, by = "zipcode", suffix=c("", ".y")) %>% select(-ends_with(".y")) %>% st_as_sf(coords = c('longitude', 'latitude'), crs = 4326)  %>%
  st_transform(st_crs(nhoods))

listings <- st_join(listings, nhoods, join = st_within, suffix=c("", ".y")) %>% select(-ends_with(".y"))

# Converting census columns into numeric
for (i in sequence(33,3,1)) {
  census[[i]] <- as.numeric(census[[i]])
}

# Grouping and summarizing census data per zip code
census <- census %>% group_by(PostalCode) %>% summarize(married = sum(Married, na.rm = TRUE), 
                                                        migration = sum(Persons_with_a_migration_background, na.rm =     TRUE),
                                                        vio_sex_crimes = sum(Violentandsexualcrimes, na.rm = TRUE),
                                                        cafes = mean(cafe_Within_1_km, na.rm = TRUE),
                                                        restaurants = mean(restaurants_Within_1_km, na.rm = TRUE),
                                                        hotels = mean(hotels_Within_5_km, na.rm = TRUE),
                                                        road = mean(Distance_to_main_road_entrance, na.rm = TRUE),
                                                        train = mean(Distance_to_train_station, na.rm = TRUE)) %>%
                                             filter(!PostalCode %in% (".")) 


# Formatting zip code correctly and changing column name
census$PostalCode <- str_extract(census$PostalCode, "^.{4}")

listings$zipcode <- str_extract(listings$zipcode, "^.{4}")  

colnames(census)[1] <- "zipcode"

# Joining listings with zip codes
listings <- left_join(listings, census, by = "zipcode")
```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Adding the number of amenities per listing
amenities_count <- as.integer(str_count(listings$amenities, ","))
amenities_count <- ifelse(amenities_count > 0, amenities_count + 1, amenities_count)

listings <- cbind(listings, amenities_count) 

# Converting columns weekly price, monthly price, cleaning fee, and security deposit to numeric values
for (i in sequence(6, 67, 1)) {
  listings[[i]] <- gsub("^.{0,1}", "", listings[[i]])
  listings[[i]] <- as.numeric(ifelse(nchar(listings[[i]]) == 0, "0", listings[[i]]) %>% str_replace(",", ""))
}

# Remove rows with no rent data
listings <- listings %>% filter(weekly_price > 0 | monthly_price > 0)

# Calculating a daily price from either weekly or monthly price
listings$daily_price <- ifelse(listings$weekly_price > 0, listings$weekly_price / 7, listings$monthly_price / 30)

# Filtering for outliers
listings <- listings %>% filter(daily_price > 0 & daily_price < 1500)

# Selecting a list of all relevant variables
var <- c("zipcode", "daily_price", "room_type", "host_is_superhost", "host_identity_verified", "accommodates", "beds", "bed_type", "cancellation_policy", "number_of_reviews", "property_type", "bathrooms", "bedrooms", "amenities_count", "review_scores_rating", "has_availability", "guests_included", "security_deposit", "cleaning_fee", "extra_people","neighbourhood", "availability_30", "weekly_price", "monthly_price", "near_ATTRAC", "near_museum", "near_Performing_arts", "married", "migration", "vio_sex_crimes", "cafes", "restaurants", "hotels", "road", "train")

listings <- listings %>% select(all_of(var)) 


# Removing NA values for important regression variables. Annotate how many we lost (Jarred)
listings <- listings %>% drop_na(cleaning_fee, security_deposit)
```

Change DESCR \## Exploratory Data Analysis

```{r read_data3, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
install.packages("psych")
library(psych)


variables_to_summarize <- c("daily_price", "room_type", 
                            "near_ATTRAC", "k_nearest_price",
                            "number_of_reviews", "property_type", 
                            "bathrooms", "bedrooms",
                            "review_scores_rating", 
                            "cancellation_policy", "host_identity_verified",
                            "accommodates", "beds", "bed_type",
                            "host_is_superhost", "cleaning_fee",
                            "security_deposit", "extra_people", 
                            "zipcode", "availability_30", "neighbourhood","distance")

summary_stats <- listings_train

summary_stats_df <- as.data.frame(summary_stats)
summary_table <- describe(summary_stats_df[, variables_to_summarize])



rounded_summary <- t(apply(summary_table, 1, function(x) {
  if (all(is.numeric(x))) {
    return(round(x, 2))
  } else {
    return(x)
  }
}))

# Create the table using kableExtra
rounded_summary %>%
  kbl(caption = "Summary Statistics") %>%
  kable_classic(full_width = F, html_font = "Cambria")


```

```{r read_datass, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Show a of the unlogged daily price (Jarred) 
gghistogram(
  data = listings, x = "daily_price", 
  add = "mean", rug = TRUE,
  fill = airbnb_color) +
  labs(title = "Daily AirBnB Price Distribution Amsterdam", caption = "Fig.1") +
   xlab("Daily Price") +
   ylab("Count") 
```

```{r read_data6, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Log price by Property Type (Jarred) 
listings$daily_price <- log(listings$daily_price)

gghistogram(
  data = listings, x = "daily_price", 
  add = "mean", rug = TRUE,
  fill = airbnb_color) +
  labs(title = "Daily AirBnB Price Distribution Amsterdam", caption = "Fig.1") +
   xlab("Daily Price") +
   ylab("Count") 

```

```{r read_data7, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Correlation Matrix (Jarred) 
corr_vars <- 
  select_if(st_drop_geometry(listings), is.numeric) %>% na.omit()

corr_vars <- select_if(st_drop_geometry(listings), is.numeric) %>%
  na.omit()

corr_vars <- corr_vars %>% select(-guests_included)

corr_vars %>% 
  correlate() %>% 
  autoplot() +
  geom_text(aes(label = round(r,digits=2)),size = 2)

```

```{r read_data8, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Log price by neighborhood (Jarred) 
listings$neighbourhood <- factor(listings$neighbourhood)


colors <- rainbow(length(unique(listings$neighbourhood)))
faded_colors <- adjustcolor(colors, alpha.f = 0.4) 

ggplot(data = listings, aes(x = neighbourhood, y = daily_price, fill = neighbourhood)) + 
  geom_boxplot() +
  scale_fill_manual(values = faded_colors, name = "Neighborhoods") + 
  theme_minimal() +
  labs(y = "Logarithm of Price", x = "", title = "Logarithm of Daily Price by Neighborhood.") +
  theme(
    axis.text.x = element_blank(), 
    legend.position = "bottom", 
    legend.title.align = 0.5, 
    plot.title = element_text(hjust = 0.5) 
  ) +
  guides(fill = guide_legend(nrow = 5, byrow = TRUE, title.position = "top")) 

```

```{r read_data9, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Log price by Room Type (Jarred) 
faded_colors2 <- adjustcolor(colors, alpha.f = 0.6) 

ggplot(data = listings, aes(x = room_type, y = daily_price, fill = room_type)) + 
  geom_boxplot() +
  scale_fill_manual(values = faded_colors2, name = "Listing Type") + 
  theme_minimal() +
  labs(y = "Logarithm of Price", x = "", title = "Logarithm of Daily Price by Listing Type") +
  theme(
    axis.text.x = element_blank(), 
    legend.position = "bottom", 
    legend.title.align = 0.5, 
    plot.title = element_text(hjust = 0.5) 
  ) +
  guides(fill = guide_legend(nrow =1, byrow = TRUE, title.position = "top")) 
```

```{r read_data99, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Checking if we have too many categories in a variable

roomtype <- unique(listings$room_type)
length(roomtype)

property_type <- unique(listings$property_type)
length(property_type)

property_type <- unique(listings$property_type)
length(property_type)

sum(is.na(listings$square_feet))

listings <- listings %>% mutate(extra_people_is_cost = ifelse(listings$extra_people %in% c("$0.00"), "No", "Yes"))



variables_to_summarize <- c("room_type", "daily_price", "beds", "accommodates", "bed_type",
                            "bathrooms", "bedrooms", "amenities_count", "review_scores_rating")


unique_values_df <- data.frame(Variable = character(), Unique_Values = integer(), stringsAsFactors = FALSE)


for (var in variables_to_summarize) {
  unique_values_df <- rbind(unique_values_df, data.frame(Variable = var, Unique_Values = length(unique(listings[[var]]))))
}


unique_values_df %>%
  kbl(caption = "Variable Values") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r map_1}
# Calculating averages per neighborhood
avg_nhood <- listings %>%
  group_by(neighbourhood) %>%
  summarize(avg_road = mean(road, na.rm = TRUE), 
            avg_cafes = mean(cafes, na.rm = TRUE), 
            avg_restaurants = mean(restaurants, na.rm = TRUE), 
            avg_hotels = mean(hotels, na.rm = TRUE), 
            avg_train=mean(train, na.rm = TRUE), 
            avg_price = exp(mean(daily_price, na.rm = TRUE)),
            avg_attrac = mean(near_ATTRAC, na.rm = TRUE),
            avg_amenities = mean(amenities_count, na.rm = TRUE))

neighbourhood_boundaries <- nhoods

# Adding neighborhood boundary info
neighbourhood_boundaries$neighbourhood <- as.character(neighbourhood_boundaries$neighbourhood)
avg_nhood$neighbourhood <- as.character(avg_nhood$neighbourhood)

merged_data_sf <- st_join(neighbourhood_boundaries, avg_nhood)

# Looping to save a map for each variable inside. We save the ggplots in the object "maps"
maps <- lapply(c("avg_price", "avg_road", "avg_cafes", "avg_restaurants", "avg_hotels", "avg_train", "avg_attrac", "avg_amenities"), function(i) {  
  ggplot()+
  geom_sf(data = merged_data_sf, aes(fill = (avg_nhood[[i]])))+
  theme_void()})

maps[[1]] +  labs(title = "Average Price", caption = "Fig.1") + 
             scale_fill_gradient(low = "white",high = airbnb_color, name = "Price Gradient in USD") +
             labs(title = "Avg. Daily AirBnB Price in Amsterdam", caption = "Fig.1")
```

```{r read_data88, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Distance to city center (why are there NA's?)
MRB <- multipleRingBuffer(st_union(listings %>% filter(neighbourhood == "Centrum-West")), 11000, 200)

listings <- st_join(listings, MRB, join = st_intersects) %>% 
            st_sf()

listings <- listings %>% mutate(distance = ifelse(listings$neighbourhood == "Centrum-West", 0, distance))

# Map of MRB and data points
ggplot() + geom_sf(data = MRB) + geom_sf(data = listings)

# Distance vs price plot
ggplot() +  geom_line(data = listings, 
                  aes(x = distance, 
                      y = daily_price), 
                      stat = "summary", 
                      fun = mean) +
         labs(title = "Median Rent as Function of Distance in Miles",
              caption = "Fig.9") +
         xlab("Distance in Miles") +
         ylab("Median Rent in US-Dollars") +
         theme_bw(base_rect_size = 2) +
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

-   public transport is good, doesn't matter where we are

# Methods & Results

Regression Variables:

Spatial Features: -nhood -k nearest neighboors price per sqft

Non-Spatial (hedonic) Features: - room type - number of reviews -
availability - is super host - identity verified - property type -
accomodates / guests_included? - bathrooms - bedrooms - break up the
amenities - sqft is not there for all - review_scores_rating - costs
extra? - is real bed? - cleaning fee - cancellation policy

# Training Regression

```{r regression, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE }
# Partitioning data set into training and test
set.seed(1000)

inTrain <- createDataPartition(
              y = paste(listings$daily_price,
                        listings$zipcode,
                        listings$neighbourhood),
              p = .6, list = FALSE)

# Filtering out factors in features that occur seldomly to avoid "new levels" error
listings_train <- listings[inTrain,] %>% filter(!room_type %in% c("Shared room"), !property_type %in% c("Boutique hotel", "Bungalow", "Cabin", "Chalet", "Nature lodge", "Villa", "Serviced apartment"), !bed_type %in% c("Airbed"))

listings_test <- listings[-inTrain,] %>% filter(!room_type %in% c("Shared room"), !property_type %in% c("Boutique hotel", "Bungalow", "Cabin", "Chalet", "Nature lodge", "Villa", "Serviced apartment"), !bed_type %in% c("Airbed"))

# Adding nearest neighbours
coords.test.training <-  st_coordinates(listings_train) 

neighborList.training <- knn2nb(knearneigh(coords.test.training, 5))

spatialWeights.training <- nb2listw(neighborList.training, style="W")


listings_train <- listings_train %>% mutate(k_nearest_price = lag.listw(spatialWeights.training, daily_price) / accommodates)

# Running regression
  reg_train <- 
    lm(daily_price ~ ., data = as.data.frame(listings_train) %>% 
                               dplyr::select(daily_price,
                                             room_type,
                                             near_ATTRAC,
                                             k_nearest_price,
                                             number_of_reviews,
                                             property_type,
                                             bathrooms,
                                             bedrooms,
                                             review_scores_rating,
                                             cancellation_policy,
                                             host_identity_verified,
                                             accommodates,
                                             beds,
                                             bed_type,
                                             host_is_superhost,
                                             cleaning_fee,
                                             security_deposit,
                                             extra_people,
                                             availability_30,
                                             zipcode,
                                             neighbourhood,
                                             distance))
  
summary(reg_train)$r.squared
```

```{r regression7, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE }
set.seed(1000)

loop <- c("daily_price", "room_type", "near_ATTRAC", "k_nearest_price", "number_of_reviews", "property_type", "bathrooms", "bedrooms", "review_scores_rating", "cancellation_policy", "host_identity_verified", "accommodates", "beds", "bed_type", "host_is_superhost", "cleaning_fee", "security_deposit", "extra_people", "availability_30", "zipcode", "neighbourhood", "distance")

results <- vector()

for (i in sequence(length(loop),1,1)) {
 words <- loop[1:i]  
 
 reg_train <- 
    lm(daily_price ~ ., data = as.data.frame(listings_train) %>% 
                               dplyr::select(words))
  
results [[i]] <- summary(reg_train)$r.squared
}

results <- as.data.frame(cbind(loop, results)) %>% mutate(lagged_results = lag(results), change = as.numeric(results) - as.numeric(lagged_results))
```

# Training Regression Results

```{r result_traiining_set7, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
# Adding Baseline Regression predictions to data set and adding KPI's
listings_train <- listings_train %>% na.omit()

listings_train <-
  listings_train %>%
  mutate(Regression = "Baseline Regression",
         daily_price.predict = predict(reg_train, listings_train),
         daily_price.error = daily_price.predict - daily_price,
         daily_price.abserror = abs(daily_price.predict - daily_price),
         daily_price.ape = (abs(daily_price.predict - daily_price)) / daily_price.predict)%>%
  filter(!is.na(daily_price.abserror))


# Saving results in table 
results_train <- data.frame(MAE = mean(listings_train$daily_price.abserror, na.rm = T), MAPE =  mean(listings_train$daily_price.ape, na.rm = T))

results_train %>%
  kbl(caption = "Training Results") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

# Test Regression

```{r read_data5, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Adding nearest neighbours
coords.test.2 <-  st_coordinates(listings_test) 

neighborList.test.2 <- knn2nb(knearneigh(coords.test.2, 3))

spatialWeights.test.2 <- nb2listw(neighborList.test.2, style="W")

listings_test <- listings_test %>% mutate(k_nearest_price = lag.listw(spatialWeights.test.2, daily_price) / accommodates)

# Applying regression model to test set and adding KPI's
listings_test <-
  listings_test %>%
  mutate(Regression = "Baseline Regression",
         daily_price.predict = predict(reg_train, listings_test),
         daily_price.error = daily_price.predict - daily_price,
         daily_price.abserror = abs(daily_price.predict - daily_price),
         daily_price.ape = (abs(daily_price.predict - daily_price)) / daily_price.predict)%>%
  filter(daily_price < 3000000, !is.na(daily_price.abserror))


# Saving results in table 
results_test <- data.frame(MAE = mean(listings_test$daily_price.abserror, na.rm = T), MAPE =  mean(listings_test$daily_price.ape, na.rm = T))

results_test %>%
  kbl(caption = "Test Results") %>%
  kable_classic(full_width = F, html_font = "Cambria")

# Visualizing spatial error
ggplot() +
  geom_sf(data = listings_test, fill ="grey40" ,colour = "white") +
  geom_sf(data = listings_test, aes(colour = q5(daily_price.error)),
          size = 1) +
  scale_colour_manual(values = palette6,
                      labels = qBr(listings_test, "daily_price.error"),
                      name = "Quintile \n Breaks")+
   labs(title = "daily_price Amsterdam") +
  mapTheme()
```

# Moran's I Test

```{r moran_mc, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
moranTest <- moran.mc(listings_test$daily_price.error, 
                      spatialWeights.test.2, nsim = 999)

morans_plot <-ggplot(as.data.frame(moranTest$res[c(1:999)]), aes(moranTest$res[c(1:999)])) +
  geom_histogram(binwidth = 0.01) +
  geom_vline(aes(xintercept = moranTest$statistic), colour = "#FA7800",size=1) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(title="Observed and permuted Moran's I",
       subtitle= "Observed Moran's I in orange",
       x="Moran's I",
       y="Count") +
  plotTheme()

morans_plot
```

## Cross-Validation

```{r result_cross_validation, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
# Specifying 100-fold CV as computational nuance
fitControl <- trainControl(method = "cv", number = 100)

set.seed(825)

# Running 100-fold CV
reg.cv <- 
  train(daily_price ~ ., data = st_drop_geometry(listings_train) %>% 
                               dplyr::select(daily_price,
                                             room_type,
                                             near_ATTRAC,
                                             k_nearest_price,
                                             number_of_reviews,
                                             property_type,
                                             bathrooms,
                                             bedrooms,
                                             review_scores_rating,
                                             cancellation_policy,
                                             host_identity_verified,
                                             accommodates,
                                             beds,
                                             bed_type,
                                             host_is_superhost,
                                             cleaning_fee,
                                             security_deposit,
                                             extra_people,
                                             availability_30,
                                             zipcode,
                                             neighbourhood,
                                             distance), 
     method = "lm", trControl = fitControl, na.action = na.pass)

reg.cv$resample[1:100,]
```

```{r result_cross_validation_graph, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
ggplot(reg.cv$resample) +
  aes(MAE) +
  geom_histogram(bins=15)
```

-   explain why we only did a count on ameniities (because they range to
    very smimilar objects)
-   justify why we predict daily price with weekly (monthly usually has
    discount, most people book for fewer days. Prove this with data)

medhh income pct education pct immigrants marital status year built
Profession distance to tourist attractions

Check instances for each variable

Questions for Michael: 1. Is our idea valid? (added variables crime
rate, percent immigrant, medhhincome, avg distance to tourist
attraction)

Can't rent multiple properties (companies need special permit) 30 nights
limit

Insights: macro features like crime rate migration are not effecting
model much since europe is more equal -\> need more data on internal
house characteristics

city could link sqaure foot to apartment sizes

Graph distance to airbnb price How can we link airbnb names to people?
Have data base!

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
#JArred
listings <- read.csv("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\listings.csv")

listings_details <- read.csv("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\listings_details.csv")

nhoods <- st_read("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\neighbourhoods.geojson")

joined <- left_join(listings, listings_details, by = "id", suffix=c("", ".y")) %>% select(-ends_with(".y"))

attraction_distance <- read.csv("C:\\Users\\fatbo\\OneDrive\\Documents\\GitHub\\Final_PPA\\Data\\Airbnb\\distance_attrac.csv")

income <- read.csv("C:\\Users\\fatbo\\OneDrive\\Documents\\GitHub\\Final_PPA\\Data\\Amsterdam_income.csv")

census <- read.csv("C:\\Users\\fatbo\\OneDrive\\Documents\\GitHub\\Final_PPA\\Data\\final_census.csv")

```
