---
title: "FairBnB"
output: html_document
date: "2023-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE, class.source = 'fold-show'}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(sf)
library(stargazer)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(kableExtra)
library(grid)
library(viridisLite)
library(viridis)
library(gridExtra)
library(jtools)
library(ggcorrplot) 
library(corrr)      
library(kableExtra)
library(jtools)     
library(ggstance) 
library(ggpubr)   
library(broom.mixed) 
options(scipen = 999)


root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

census_api_key("a6d692af505769f28e39a3ac16b7dcbacb1dad58", overwrite = TRUE)

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")

palette6 <- c("#25CB10", "#5AB60C", "grey40",   "grey40", "#FA7800")

airbnb_color <- c("#FF5A5F")

theme_update(plot.title = element_text(hjust = 0.5))
```

# Intro

# Data
## Data Import
```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
listings <- read.csv("/Users/nohman/Documents/GitHub/PPA_Final_Airbnb/Data/Airbnb/listings.csv")

nhoods <- st_read("/Users/nohman/Documents/GitHub/PPA_Final_Airbnb/Data/Airbnb/neighbourhoods.geojson")

attraction_distance <- read.csv("/Users/nohman/Documents/GitHub/Final_PPA/Data/Airbnb/distance_attrac.csv")

listings_details <- read.csv("/Users/nohman/Documents/GitHub/PPA_Final_Airbnb/Data/Airbnb/listings_details.csv")

income <- read.csv("/Users/nohman/Documents/GitHub/Final_PPA/Data/Amsterdam_income.csv")

census <- read.csv("/Users/nohman/Documents/GitHub/Final_PPA/Data/final_census.csv")
```

joined2 <- inner_join(joined, attraction_distance, by = "zipcode")

unique_nhoods <- as.data.frame(unique(joined$neighbourhood_cleansed))

join nhood to joined


## Data Wrangling
``` {r joined_nhood sf}
# Joining data sets, converting to crs
attraction_distance <- attraction_distance %>% transform(zipcode = as.character(zipcode))

listings <- left_join(listings, listings_details, by = "id", suffix=c("", ".y")) %>% select(-ends_with(".y"))

listings <- left_join(listings, attraction_distance, by = "zipcode", suffix=c("", ".y")) %>% select(-ends_with(".y")) %>% st_as_sf(coords = c('longitude', 'latitude'), crs = 4326)  %>%
  st_transform(st_crs(nhoods))

listings <- st_join(listings, nhoods, join = st_within, suffix=c("", ".y")) %>% select(-ends_with(".y"))

# Converting census columns into numeric
for (i in sequence(33,3,1)) {
  census[[i]] <- as.numeric(census[[i]])
}

# Grouping and summarizing census data per zip code
census <- census %>% group_by(PostalCode) %>% summarize(married = sum(Married, na.rm = TRUE), 
                                                        migration = sum(Persons_with_a_migration_background, na.rm =     TRUE),
                                                        vio_sex_crimes = sum(Violentandsexualcrimes, na.rm = TRUE),
                                                        cafes = mean(cafe_Within_1_km, na.rm = TRUE),
                                                        restaurants = mean(restaurants_Within_1_km, na.rm = TRUE),
                                                        hotels = mean(hotels_Within_5_km, na.rm = TRUE),
                                                        road = mean(Distance_to_main_road_entrance, na.rm = TRUE),
                                                        train = mean(Distance_to_train_station, na.rm = TRUE)) %>%
                                             filter(!PostalCode %in% (".")) 


# Formatting zip code correctly and changing column name
census$PostalCode <- str_extract(census$PostalCode, "^.{4}")

listings$zipcode <- str_extract(listings$zipcode, "^.{4}")  

colnames(census)[1] <- "zipcode"

# Joining listings with zip codes
listings <- left_join(listings, census, by = "zipcode")
```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Adding the number of amenities per listing
amenities_count <- as.integer(str_count(listings$amenities, ","))
amenities_count <- ifelse(amenities_count > 0, amenities_count + 1, amenities_count)

listings <- cbind(listings, amenities_count) 

# Converting columns weekly price, monthly price, cleaning fee, and security deposit to numeric values
for (i in sequence(6, 67, 1)) {
  listings[[i]] <- gsub("^.{0,1}", "", listings[[i]])
  listings[[i]] <- as.numeric(ifelse(nchar(listings[[i]]) == 0, "0", listings[[i]]) %>% str_replace(",", ""))
}

# Remove rows with no rent data
listings <- listings %>% filter(weekly_price > 0 | monthly_price > 0)

# Calculating a daily price from either weekly or monthly price
listings$daily_price <- ifelse(listings$weekly_price > 0, listings$weekly_price / 7, listings$monthly_price / 30)

# Filtering for outliers
listings <- listings %>% filter(daily_price > 0 & daily_price < 1500)

# Selecting a list of all relevant variables
var <- c("zipcode", "daily_price", "room_type", "host_is_superhost", "host_identity_verified", "accommodates", "beds", "bed_type", "cancellation_policy", "number_of_reviews", "property_type", "bathrooms", "bedrooms", "amenities_count", "review_scores_rating", "has_availability", "guests_included", "security_deposit", "cleaning_fee", "extra_people","neighbourhood", "availability_30", "weekly_price", "monthly_price", "near_ATTRAC", "near_museum", "near_Performing_arts", "married", "migration", "vio_sex_crimes", "cafes", "restaurants", "hotels", "road", "train")

listings <- listings %>% select(all_of(var)) 


# Removing NA values for important regression variables. Annotate how many we lost (Jarred)
listings <- listings %>% drop_na(cleaning_fee, security_deposit)
```

## Exploratory Data Analysis
```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Please rewrite without summarytools package
variables_to_summarize <- c("daily_price","room_type","near_ATTRAC", "k_nearest_price",
                            "number_of_reviews","property_type", "bathrooms", "bedrooms",
                            "review_scores_rating", "cancellation_policy", "host_identity_verified",
                            "accommodates", "beds", "bed_type", "host_is_superhost", "cleaning_fee",
                            "security_deposit", "extra_people", "zipcode", "availability_30", "neighbourhood")


summary_stats <- descr(listings[, variables_to_summarize], stats = "common")  
summary_table <- t(summary_stats)


rounded_summary <- t(apply(summary_table, 1, function(x) {
  if (all(is.numeric(x))) {
    return(round(x, 2))
  } else {
    return(x)
  }
}))

# Create the table using kableExtra
rounded_summary %>%
  kbl(caption = "Summary Statistics") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Show a of the unlogged daily price (Jarred) 
gghistogram(
  data = listings, x = "daily_price", 
  add = "mean", rug = TRUE,
  fill = airbnb_color) +
  labs(title = "Daily AirBnB Price Distribution Amsterdam", caption = "Fig.1") +
   xlab("Daily Price") +
   ylab("Count") 
```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Log price by Property Type (Jarred) 
listings$daily_price <- log(listings$daily_price)

gghistogram(
  data = listings, x = "daily_price", 
  add = "mean", rug = TRUE,
  fill = airbnb_color) +
  labs(title = "Daily AirBnB Price Distribution Amsterdam", caption = "Fig.1") +
   xlab("Daily Price") +
   ylab("Count") 

```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Correlation Matrix (Jarred) 
corr_vars <- 
  select_if(st_drop_geometry(listings), is.numeric) %>% na.omit()

corr_vars <- select_if(st_drop_geometry(listings), is.numeric) %>%
  na.omit()

corr_vars <- corr_vars %>% select(-guests_included)

corr_vars %>% 
  correlate() %>% 
  autoplot() +
  geom_text(aes(label = round(r,digits=2)),size = 2)

```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Log price by neighborhood (Jarred) 
listings$neighbourhood <- factor(listings$neighbourhood)


colors <- rainbow(length(unique(listings$neighbourhood)))
faded_colors <- adjustcolor(colors, alpha.f = 0.4) 

ggplot(data = listings, aes(x = neighbourhood, y = daily_price, fill = neighbourhood)) + 
  geom_boxplot() +
  scale_fill_manual(values = faded_colors, name = "Neighborhoods") + 
  theme_minimal() +
  labs(y = "Logarithm of Price", x = "", title = "Logarithm of Daily Price by Neighborhood.") +
  theme(
    axis.text.x = element_blank(), 
    legend.position = "bottom", 
    legend.title.align = 0.5, 
    plot.title = element_text(hjust = 0.5) 
  ) +
  guides(fill = guide_legend(nrow = 5, byrow = TRUE, title.position = "top")) 

```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Log price by Room Type (Jarred) 
faded_colors2 <- adjustcolor(colors, alpha.f = 0.6) 

ggplot(data = listings, aes(x = room_type, y = daily_price, fill = room_type)) + 
  geom_boxplot() +
  scale_fill_manual(values = faded_colors2, name = "Listing Type") + 
  theme_minimal() +
  labs(y = "Logarithm of Price", x = "", title = "Logarithm of Daily Price by Listing Type") +
  theme(
    axis.text.x = element_blank(), 
    legend.position = "bottom", 
    legend.title.align = 0.5, 
    plot.title = element_text(hjust = 0.5) 
  ) +
  guides(fill = guide_legend(nrow =1, byrow = TRUE, title.position = "top")) 
```


```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Checking if we have too many categories in a variable

roomtype <- unique(listings$room_type)
length(roomtype)

property_type <- unique(listings$property_type)
length(property_type)

property_type <- unique(listings$property_type)
length(property_type)

sum(is.na(listings$square_feet))

listings <- listings %>% mutate(extra_people_is_cost = ifelse(listings$extra_people %in% c("$0.00"), "No", "Yes"))



variables_to_summarize <- c("room_type", "daily_price", "beds", "accommodates", "bed_type",
                            "bathrooms", "bedrooms", "amenities_count", "review_scores_rating")


unique_values_df <- data.frame(Variable = character(), Unique_Values = integer(), stringsAsFactors = FALSE)


for (var in variables_to_summarize) {
  unique_values_df <- rbind(unique_values_df, data.frame(Variable = var, Unique_Values = length(unique(listings[[var]]))))
}


unique_values_df %>%
  kbl(caption = "Variable Values") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

```{r map_1}
# Calculating averages per neighborhood
avg_nhood <- listings %>%
  group_by(neighbourhood) %>%
  summarize(avg_road = mean(road, na.rm = TRUE), 
            avg_cafes = mean(cafes, na.rm = TRUE), 
            avg_restaurants = mean(restaurants, na.rm = TRUE), 
            avg_hotels = mean(hotels, na.rm = TRUE), 
            avg_train=mean(train, na.rm = TRUE), 
            avg_price = exp(mean(daily_price, na.rm = TRUE)),
            avg_attrac = mean(near_ATTRAC, na.rm = TRUE),
            avg_amenities = mean(amenities_count, na.rm = TRUE))

neighbourhood_boundaries <- nhoods

# Adding neighborhood boundary info
neighbourhood_boundaries$neighbourhood <- as.character(neighbourhood_boundaries$neighbourhood)
avg_nhood$neighbourhood <- as.character(avg_nhood$neighbourhood)

merged_data_sf <- st_join(neighbourhood_boundaries, avg_nhood)

# Looping to save a map for each variable inside. We save the ggplots in the object "maps"
maps <- lapply(c("avg_price", "avg_road", "avg_cafes", "avg_restaurants", "avg_hotels", "avg_train", "avg_attrac", "avg_amenities"), function(i) {  
  ggplot()+
  geom_sf(data = merged_data_sf, aes(fill = (avg_nhood[[i]])))+
  theme_void()})

maps[[1]] +  labs(title = "Average Price", caption = "Fig.1") + 
             scale_fill_gradient(low = "white",high = airbnb_color, name = "Price Gradient in USD") +
             labs(title = "Avg. Daily AirBnB Price in Amsterdam", caption = "Fig.1")
```


```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Distance to city center (why are there NA's?)
MRB <- multipleRingBuffer(st_union(listings %>% filter(neighbourhood == "Centrum-West")), 11000, 200)

listings <- st_join(listings, MRB, join = st_intersects) %>% 
            st_sf()

listings <- listings %>% mutate(distance = ifelse(listings$neighbourhood == "Centrum-West", 0, distance))

# Map of MRB and data points
ggplot() + geom_sf(data = MRB) + geom_sf(data = listings)

# Distance vs price plot
ggplot() +  geom_line(data = listings, 
                  aes(x = distance, 
                      y = daily_price), 
                      stat = "summary", 
                      fun = mean) +
         labs(title = "Median Rent as Function of Distance in Miles",
              caption = "Fig.9") +
         xlab("Distance in Miles") +
         ylab("Median Rent in US-Dollars") +
         theme_bw(base_rect_size = 2) +
         theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

- public transport is good, doesn't matter where we are 

# Methods & Results


Regression Variables:

Spatial Features:
-nhood
-k nearest neighboors price per sqft

Non-Spatial (hedonic) Features:
- room type
- number of reviews
- availability
- is super host
- identity verified
- property type
- accomodates / guests_included?
- bathrooms
- bedrooms
- break up the amenities
- sqft is not there for all
- review_scores_rating
- costs extra?
- is real bed?
- cleaning fee
- cancellation policy 

# Training Regression

```{r regression, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE }
# Partitioning data set into training and test
set.seed(1000)

inTrain <- createDataPartition(
              y = paste(listings$daily_price,
                        listings$zipcode,
                        listings$neighbourhood),
              p = .6, list = FALSE)

# Filtering out factors in features that occur seldomly to avoid "new levels" error
listings_train <- listings[inTrain,] %>% filter(!room_type %in% c("Shared room"), !property_type %in% c("Boutique hotel", "Bungalow", "Cabin", "Chalet", "Nature lodge", "Villa", "Serviced apartment"), !bed_type %in% c("Airbed"))

listings_test <- listings[-inTrain,] %>% filter(!room_type %in% c("Shared room"), !property_type %in% c("Boutique hotel", "Bungalow", "Cabin", "Chalet", "Nature lodge", "Villa", "Serviced apartment"), !bed_type %in% c("Airbed"))

# Adding nearest neighbours
coords.test.training <-  st_coordinates(listings_train) 

neighborList.training <- knn2nb(knearneigh(coords.test.training, 5))

spatialWeights.training <- nb2listw(neighborList.training, style="W")


listings_train <- listings_train %>% mutate(k_nearest_price = lag.listw(spatialWeights.training, daily_price) / accommodates)

# Running regression
  reg_train <- 
    lm(daily_price ~ ., data = as.data.frame(listings_train) %>% 
                               dplyr::select(daily_price,
                                             room_type,
                                             near_ATTRAC,
                                             k_nearest_price,
                                             number_of_reviews,
                                             property_type,
                                             bathrooms,
                                             bedrooms,
                                             review_scores_rating,
                                             cancellation_policy,
                                             host_identity_verified,
                                             accommodates,
                                             beds,
                                             bed_type,
                                             host_is_superhost,
                                             cleaning_fee,
                                             security_deposit,
                                             extra_people,
                                             availability_30,
                                             zipcode,
                                             neighbourhood,
                                             distance))
  
summary(reg_train)$r.squared
```

```{r regression, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE }
set.seed(1000)

loop <- c("daily_price", "room_type", "near_ATTRAC", "k_nearest_price", "number_of_reviews", "property_type", "bathrooms", "bedrooms", "review_scores_rating", "cancellation_policy", "host_identity_verified", "accommodates", "beds", "bed_type", "host_is_superhost", "cleaning_fee", "security_deposit", "extra_people", "availability_30", "zipcode", "neighbourhood", "distance")

results <- vector()

for (i in sequence(length(loop),1,1)) {
 words <- loop[1:i]  
 
 reg_train <- 
    lm(daily_price ~ ., data = as.data.frame(listings_train) %>% 
                               dplyr::select(words))
  
results [[i]] <- summary(reg_train)$r.squared
}

results <- as.data.frame(cbind(loop, results)) %>% mutate(lagged_results = lag(results), change = as.numeric(results) - as.numeric(lagged_results))
```

# Training Regression Results
```{r result_traiining_set, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
# Adding Baseline Regression predictions to data set and adding KPI's
listings_train <- listings_train %>% na.omit()

listings_train <-
  listings_train %>%
  mutate(Regression = "Baseline Regression",
         daily_price.predict = predict(reg_train, listings_train),
         daily_price.error = daily_price.predict - daily_price,
         daily_price.abserror = abs(daily_price.predict - daily_price),
         daily_price.ape = (abs(daily_price.predict - daily_price)) / daily_price.predict)%>%
  filter(!is.na(daily_price.abserror))


# Saving results in table 
results_train <- data.frame(MAE = mean(listings_train$daily_price.abserror, na.rm = T), MAPE =  mean(listings_train$daily_price.ape, na.rm = T))

results_train %>%
  kbl(caption = "Training Results") %>%
  kable_classic(full_width = F, html_font = "Cambria")
```

# Test Regression
```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Adding nearest neighbours
coords.test.2 <-  st_coordinates(listings_test) 

neighborList.test.2 <- knn2nb(knearneigh(coords.test.2, 3))

spatialWeights.test.2 <- nb2listw(neighborList.test.2, style="W")

listings_test <- listings_test %>% mutate(k_nearest_price = lag.listw(spatialWeights.test.2, daily_price) / accommodates)

# Applying regression model to test set and adding KPI's
listings_test <-
  listings_test %>%
  mutate(Regression = "Baseline Regression",
         daily_price.predict = predict(reg_train, listings_test),
         daily_price.error = daily_price.predict - daily_price,
         daily_price.abserror = abs(daily_price.predict - daily_price),
         daily_price.ape = (abs(daily_price.predict - daily_price)) / daily_price.predict)%>%
  filter(daily_price < 3000000, !is.na(daily_price.abserror))


# Saving results in table 
results_test <- data.frame(MAE = mean(listings_test$daily_price.abserror, na.rm = T), MAPE =  mean(listings_test$daily_price.ape, na.rm = T))

results_test %>%
  kbl(caption = "Test Results") %>%
  kable_classic(full_width = F, html_font = "Cambria")

# Visualizing spatial error
ggplot() +
  geom_sf(data = listings_test, fill ="grey40" ,colour = "white") +
  geom_sf(data = listings_test, aes(colour = q5(daily_price.error)),
          size = 1) +
  scale_colour_manual(values = palette6,
                      labels = qBr(listings_test, "daily_price.error"),
                      name = "Quintile \n Breaks")+
   labs(title = "daily_price Amsterdam") +
  mapTheme()
```


# Moran's I Test
```{r moran_mc, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
moranTest <- moran.mc(listings_test$daily_price.error, 
                      spatialWeights.test.2, nsim = 999)

morans_plot <-ggplot(as.data.frame(moranTest$res[c(1:999)]), aes(moranTest$res[c(1:999)])) +
  geom_histogram(binwidth = 0.01) +
  geom_vline(aes(xintercept = moranTest$statistic), colour = "#FA7800",size=1) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(title="Observed and permuted Moran's I",
       subtitle= "Observed Moran's I in orange",
       x="Moran's I",
       y="Count") +
  plotTheme()

morans_plot
```


## Cross-Validation
```{r result_cross_validation, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
# Specifying 100-fold CV as computational nuance
fitControl <- trainControl(method = "cv", number = 100)

set.seed(825)

# Running 100-fold CV
reg.cv <- 
  train(daily_price ~ ., data = st_drop_geometry(listings_train) %>% 
                               dplyr::select(daily_price,
                                             room_type,
                                             near_ATTRAC,
                                             k_nearest_price,
                                             number_of_reviews,
                                             property_type,
                                             bathrooms,
                                             bedrooms,
                                             review_scores_rating,
                                             cancellation_policy,
                                             host_identity_verified,
                                             accommodates,
                                             beds,
                                             bed_type,
                                             host_is_superhost,
                                             cleaning_fee,
                                             security_deposit,
                                             extra_people,
                                             availability_30,
                                             zipcode,
                                             neighbourhood,
                                             distance), 
     method = "lm", trControl = fitControl, na.action = na.pass)

reg.cv$resample[1:100,]
```



```{r result_cross_validation_graph, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
ggplot(reg.cv$resample) +
  aes(MAE) +
  geom_histogram(bins=15)
```









- explain why we only did a count on ameniities (because they range to very smimilar objects)
- justify why we predict daily price with weekly (monthly usually has discount, most people book for fewer days. Prove this with data)


medhh income
pct education
pct immigrants
marital status
year built
Profession
distance to tourist attractions



Check instances for each variable


Questions for Michael:
1. Is our idea valid? (added variables crime rate, percent immigrant, medhhincome, avg distance to tourist attraction)


Can't rent multiple properties (companies need special permit)
30 nights limit

Insights: macro features like crime rate migration are not effecting model much since europe is more equal -> need more data on internal house characteristics

city could link sqaure foot to apartment sizes

Graph distance to airbnb price 
How can we link airbnb names to people? Have data base! 



