---
title: "Fairbnb"
output: html_document
date: "2023-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE, class.source = 'fold-show'}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(sf)
library(stargazer)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(kableExtra)
library(grid)
library(viridisLite)
library(viridis)
library(gridExtra)
library(jtools)
library(ggcorrplot) 
library(corrr)      
library(kableExtra)
library(jtools)     
library(ggstance) 
library(ggpubr)   
library(broom.mixed) 
options(scipen = 999)


root.dir = "https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/DATA/"

source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

census_api_key("a6d692af505769f28e39a3ac16b7dcbacb1dad58", overwrite = TRUE)

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")

palette6 <- c("#25CB10", "#5AB60C", "grey40",   "grey40", "#FA7800")

theme_update(plot.title = element_text(hjust = 0.5))



```

# Intro

# Data



join nhood to joined

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
#Nohman
listings <- read.csv("/Users/nohman/Documents/GitHub/PPA_Final_Airbnb/Data/Airbnb/listings.csv")

listings_details <- read.csv("/Users/nohman/Documents/GitHub/PPA_Final_Airbnb/Data/Airbnb/listings_details.csv")

nhoods <- st_read("/Users/nohman/Documents/GitHub/PPA_Final_Airbnb/Data/Airbnb/neighbourhoods.geojson")

joined <- left_join(listings, listings_details, by = "id", suffix=c("", ".y")) %>% select(-ends_with(".y"))

unique_nhoods <- as.data.frame(unique(joined$neighbourhood_cleansed))

joined2 <- inner_join(joined, attraction_distance, by = "zipcode")





```




join nhood to joined



``` {r joined_nhood sf}



joined <- st_as_sf(joined, coords = c('longitude', 'latitude'), crs = 4326)  %>%
  st_transform(st_crs(nhoods))
  

joined <- st_join(joined, nhoods, join = st_within)

st_crs(nhoods)
```


View(nhoods)
- Add sentiment analysis 
- Add tract info


# OLS Regression Model

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Checking if we have too many categories in a variable
roomtype <- unique(joined$room_type)
length(roomtype)

property_type <- unique(joined$property_type)
length(property_type)

sum(is.na(joined$square_feet))

joined <- joined %>% mutate(extra_people_is_cost = ifelse(joined$extra_people %in% c("$0.00"), "No", "Yes"))


```

```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
# Creating amenities count. +1 since last word doesn't have comma



amenities_count <- as.integer(str_count(joined$amenities, ","))
amenities_count <- ifelse(amenities_count > 0, amenities_count + 1, amenities_count)

joined <- cbind(joined, amenities_count) 
View(joined)

# do this with mutate



joined$weekly_price <- gsub("^.{0,1}", "", joined$weekly_price)
joined$weekly_price <- as.numeric(ifelse(nchar(joined$weekly_price) == 0, "0", joined$weekly) %>% str_replace(",", ""))

joined$monthly_price <- gsub("^.{0,1}", "", joined$weekly_price)
joined$monthly_price <- as.numeric(ifelse(nchar(joined$monthly_price) == 0, "0", joined$monthly) %>% str_replace(",", ""))

joined$security_deposit<- gsub("^.{0,1}", "", joined$security_deposit)
joined$security_deposit <- as.numeric(ifelse(nchar(joined$security_deposit) == 0, NA, joined$security_deposit) %>% str_replace(",", ""))

joined$cleaning_fee<- gsub("^.{0,1}", "", joined$cleaning_fee)
joined$cleaning_fee <- as.numeric(ifelse(nchar(joined$cleaning_fee) == 0, NA, joined$cleaning_fee) %>% str_replace(",", ""))

joined$daily_price <- ifelse(joined$weekly_price > 0, joined$weekly_price / 7, joined$monthly_price / 30)

#joined$zipcode <- ifelse(str_count(joined$zipcode, "") != 0, str_extract(joined$zipcode, "^.{6}"), str_extract(joined$zipcode, "^.{4}"))

joined$zipcode <- str_extract(joined$zipcode, "^.{4}")
  

joined <- joined %>% filter(daily_price > 0 & daily_price < 1500)


var <- c("zipcode", "daily_price", "room_type", "host_is_superhost", "host_identity_verified", "accommodates", "beds", "bed_type", "cancellation_policy", "number_of_reviews", "property_type", "bathrooms", "bedrooms", "amenities_count", "review_scores_rating", "has_availability", "guests_included", "security_deposit", "cleaning_fee", "extra_people","neighbourhood.x", "availability_30")

joined <- joined %>% select(all_of(var))

joined$daily_price <- log(joined$daily_price)

joined <- joined %>% drop_na(cleaning_fee, security_deposit)





```

# Methods & Results


Regression Variables:

Spatial Features:
-nhood
-k nearest neighboors price per sqft

Non-Spatial (hedonic) Features:
- room type
- number of reviews
- availability
- is super host
- identity verified
- property type
- accomodates / guests_included?
- bathrooms
- bedrooms
- break up the amenities
- sqft is not there for all
- review_scores_rating
- costs extra?
- is real bed?
- cleaning fee
- cancellation policy 

# Training Regression

```{r regression, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE }
set.seed(100)

inTrain <- createDataPartition(
              y = paste(joined$daily_price,
                        joined$room_type,
                        joined$number_of_reviews),
              p = .60, list = FALSE)

joined_training <- joined[inTrain,] 

joined_test <- joined[-inTrain,] 


coords.test.training <-  st_coordinates(joined_training) 

neighborList.training <- knn2nb(knearneigh(coords.test.training, 10))

spatialWeights.training <- nb2listw(neighborList.training, style="W")


joined_training <- joined_training %>% mutate(k_nearest_price = lag.listw(spatialWeights.training, daily_price) / accommodates)


  reg_training <- 
    lm(daily_price ~ ., data = as.data.frame(joined_training) %>% 
                               dplyr::select(daily_price,
                                           room_type,
                                           k_nearest_price,
                                           number_of_reviews,
                                           property_type,
                                           bathrooms,
                                           bedrooms,
                                           review_scores_rating,
                                           cancellation_policy,
                                           host_identity_verified,
                                           accommodates,
                                           beds,
                                           bed_type,
                                           host_is_superhost,
                                           cleaning_fee,
                                           security_deposit,
                                           extra_people,
                                           zipcode,
                                           availability_30,
                                           neighbourhood.x))
  
summary(reg_training)$r.squared
```

# Training Regression Results

```{r result_traiining_set, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
joined_training <-
  joined_training %>%
  mutate(Regression = "Baseline Regression",
         daily_price.predict = exp(predict(reg_training, joined_training)),
         daily_price.error = daily_price.predict - exp(daily_price),
         daily_price.abserror = abs(daily_price.predict - exp(daily_price)),
         daily_price.ape = (abs(daily_price.predict - exp(daily_price))) / daily_price.predict)%>%
  filter(daily_price < 3000000, !is.na(daily_price.abserror))

results_train <- data.frame(MAE = mean(joined_training$sale_price.abserror, na.rm = T), MAPE =  mean(joined_training$sale_price.ape, na.rm = T))


results_train %>%
  kbl(caption = "Training Results") %>%
  kable_classic(full_width = F, html_font = "Cambria")

```

# Test Regression
```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}

coords.test.2 <-  st_coordinates(joined_test) 

neighborList.test.2 <- knn2nb(knearneigh(coords.test.2, 3))

spatialWeights.test.2 <- nb2listw(neighborList.test.2, style="W")

joined_test <- joined_test %>% mutate(k_nearest_price = lag.listw(spatialWeights.test.2, daily_price) / accommodates)

joined_test <-
  joined_test %>%
  mutate(Regression = "Baseline Regression",
         daily_price.predict = exp(predict(reg_training, joined_test)),
         daily_price.error = daily_price.predict - exp(daily_price),
         daily_price.abserror = abs(daily_price.predict - exp(daily_price)),
         daily_price.ape = (abs(daily_price.predict - exp(daily_price))) / daily_price.predict)%>%
  filter(daily_price < 3000000, !is.na(daily_price.abserror))


ggplot() +
  geom_sf(data = joined, fill ="grey40" ,colour = "white") +
  geom_sf(data = joined_test, aes(colour = q5(daily_price.error)),
          size = 1) +
  scale_colour_manual(values = palette6,
                      labels = qBr(joined_test, "daily_price.error"),
                      name = "Quintile \n Breaks")+
   labs(title = "daily_price Amsterdam") +
  mapTheme()
```


# Moran's I Test
```{r moran_mc, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}

moranTest <- moran.mc(joined_test$daily_price.error, 
                      spatialWeights.test.2, nsim = 999)

morans_plot <-ggplot(as.data.frame(moranTest$res[c(1:999)]), aes(moranTest$res[c(1:999)])) +
  geom_histogram(binwidth = 0.01) +
  geom_vline(aes(xintercept = moranTest$statistic), colour = "#FA7800",size=1) +
  scale_x_continuous(limits = c(-1, 1)) +
  labs(title="Observed and permuted Moran's I",
       subtitle= "Observed Moran's I in orange",
       x="Moran's I",
       y="Count") +
  plotTheme()

morans_plot
```


## Cross-Validation
```{r result_cross_validation, results = 'hide', fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
fitControl <- trainControl(method = "cv", number = 100)
set.seed(825)

reg.cv <- 
  train(sale_price ~ ., data = st_drop_geometry(philly.training) %>% 
                               dplyr::select(sale_price, 
                                             k_nearest_price,
                                             pctWhite.2020,
                                             pctGrad.2020,
                                             med_HH_Income.2020,  
                                             total_livable_area,
                                             frontage, 
                                             exterior_condition,
                                             interior_condition,
                                             number_of_bathrooms,
                                             quality_grade,
                                             basements,
                                             garage_spaces,
                                             sewer, separate_utilities,
                                             street_designation,
                                             building_code_description_new, 
                                             view_type, 
                                             general_construction, 
                                             stories, 
                                             number_of_bedrooms), 
     method = "lm", trControl = fitControl, na.action = na.pass)

reg.cv$resample[1:100,]




```



```{r result_cross_validation_graph, fig.align= 'center', warning = FALSE, message = FALSE, error = FALSE}
ggplot(reg.cv$resample) +
  aes(MAE) +
  geom_histogram(bins=15)
```









- explain why we only did a count on ameniities (because they range to very smimilar objects)
- justify why we predict daily price with weekly (monthly usually has discount, most people book for fewer days. Prove this with data)


medhh income
pct education
pct immigrants
marital status
year built
Profession
distance to tourist attractions



Check instances for each variable



Questions for Michael:
1. Wants to see process of varibale choice (i.e. we run regression and then drop variables etc?)
2. Is our idea valid?
3. How does regression handle NA




```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
#JArred
listings <- read.csv("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\listings.csv")

listings_details <- read.csv("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\listings_details.csv")

nhoods <- st_read("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\neighbourhoods.geojson")

joined <- left_join(listings, listings_details, by = "id", suffix=c("", ".y")) %>% select(-ends_with(".y"))

```



```{r read_data, results = FALSE, message = FALSE, warning = FALSE, error = FALSE}
#JArred
listings <- read.csv("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\listings.csv")

listings_details <- read.csv("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\listings_details.csv")

nhoods <- st_read("C:\\Users\\fatbo\\OneDrive\\Desktop\\Airbnb\\Airbnb\\neighbourhoods.geojson")

joined <- left_join(listings, listings_details, by = "id", suffix=c("", ".y")) %>% select(-ends_with(".y"))

attraction_distance <- read.csv("C:\\Users\\fatbo\\OneDrive\\Documents\\GitHub\\Final_PPA\\Data\\Airbnb\\distance_attrac.csv")

```